Curiosity-Driven Development of Tool Use Precursors: a Robotic Model

### 2016-01-31 cogsci2016/paper.tex
figures

	\begin{figure}[ht]
		\centering
		\subfloat{\includegraphics[width=4.5cm]{./include/H-RGB-P-AMB-log9-interests-100000.pdf}}
		\hspace{-0.7cm}
		\subfloat{\includegraphics[width=4.5cm]{./include/H-RGB-P-AMB-log9-obj-explo.pdf}}
		\caption{Condition H-P-AMB. Left: Interests of each model. Right: Exploration of the object space: each dot is one point reached with the object at the end of a movement.}
		\label{res_interests}
	\end{figure}

@@

		\begin{figure*}[ht]
			\centering
			\includegraphics[width=5.5cm]{./include/F-RGB-log53-events-100000.pdf}
			\hspace{-0.4cm}
			\includegraphics[width=5.5cm]{./include/H-RGB-GR-AMB-log15-events-100000.pdf}
			\hspace{-0.4cm}
			\includegraphics[width=5.5cm]{./include/H-RGB-P-AMB-log8-events-100000.pdf}
			\caption{Behavioural phases typical exemples. Left: F-RGB. Middle: H-GR-AMB, Right: H-P-AMB. Only hierarchical active condition H-P-AMB shows overlapping phases of behaviour similar to infant development.}
			\label{res_ow}
		\end{figure*}

@@

		\begin{figure}[ht]
			\centering
			\includegraphics[width=4.5cm]{./include/H-RGB-P-AMB-log9-choice_mod4.png}
			\hspace{-0.6cm}
			\includegraphics[width=4.5cm]{./include/H-RGB-P-AMB-PGITC-log3-choice_mod4.png}
			\caption{Chosen tool depending on object goal position. Blue points: long stick choice. Red points: small stick choice. Left: condition H-P-AMB, strong boundaries 
			between tool choice regions. Right: condition H-P-AMB-ATC, parallel exploration of both tools for the same goals.}
			\label{res_choice}
		\end{figure}

>>>>

	\begin{figure}[ht]
		\centering
		\hspace{-0.7cm}	
		\vspace{0pt}
		\includegraphics[width=4.4cm]{./include/H-RGB-P-AMB-log9-interests-100000.png}
		\hspace{-0.1cm}	
		%\vspace{-0.2cm}
		\vspace{0pt}
		\includegraphics[width=4.26cm]{./include/obj-explo.pdf}
		\caption{Condition H-P-AMB. Left: Interests of each model. Right: Exploration of the object space: each dot is one point reached with the object at the end of a movement.}
		\label{res_interests}
	\end{figure}

@@

		\begin{figure*}[ht]
			\centering
			\includegraphics[width=5.5cm]{./include/F-RGB-log53-events-100000.pdf}
			\hspace{-0.4cm}
			\includegraphics[width=5.5cm]{./include/H-RGB-GR-AMB-log13-events-100000.pdf}
			\hspace{-0.4cm}
			\includegraphics[width=5.5cm]{./include/H-RGB-P-AMB-log38-events-100000.pdf}
			\caption{Behavioural phases typical exemples. Left: F-RGB. Middle: H-GR-AMB, Right: H-P-AMB. Only hierarchical active condition H-P-AMB shows overlapping phases of behaviour similar to infant development.}
			\label{res_ow}
		\end{figure*}

@@

		\begin{figure}[ht]
			\centering
			\includegraphics[width=4.3cm]{./include/choice-H-RGB-P-AMB.pdf}
			\hspace{-0.2cm}
			\includegraphics[width=4.3cm]{./include/choice-H-RGB-P-AMB-PGITC.pdf}
			\caption{Chosen tool depending on object goal position. Blue points: long stick choice. Red points: small stick choice. Left: condition H-P-AMB, strong boundaries 
			between tool choice regions. Right: condition H-P-AMB-ATC, parallel exploration of both tools for the same goals.}
			\label{res_choice}
		\end{figure}
